# Storm tracking for Real Projections

An R package to analyse and plot storm tracks and storm track density from reanalyses and climate model data.

The package uses `data.table` and `ggplot2` for fast computation and high quality graphics.


## Installation

```{r, eval=FALSE}
devtools::install_github('sieste/realstorms')
library(realstorms)
```
```{r, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=3.5, fig.path='figure/readme/')
devtools::install()
library(realstorms)
```


## Usage example

We are working with files of standard ascii output format produced by the
[TRACK storm tracking
software](http://www.nerc-essc.ac.uk/~kih/TRACK/Track.html). (Currently, no data is included with the package, but will soon be.)


```{r init-file}
stormsfile = 'storms.txt'
writeLines(readLines(stormsfile, n=8))
```

The function `read_tracks` parses TRACK output into a `data.table`. Variable names can be passed as a function argument:

```{r read-file}
trx = read_tracks(stormsfile, var=c('vor850', 'mslp', 'speed', 'precip', 'omega'))
head(trx)
```


The function `track_density` splits the world up into grid boxes of width and height `bw` (in degrees) and calculates track count, track density, feature count and feature density:

```{r calc-td}
# calculate track density on a 5x5 degree grid
td = track_density(trx, bw=5)
head(td)
```

The object `trx` is of class `stormtracks`, and the object `td` is of class `track_density`. Both classes have S3 plotting methods:

```{r plot-trx}
plot(trx, var='vor850')
```

```{r plot-td}
plot(td, 'track_density')
```


```{r plot-fc}
plot(td, 'feature_count')
```



